Methods for Large Scale Learning to Rank

### 2014-05-01 report/Chapters/CrossBenchmarkComparison.tex
feedback Sander verwerkt

As we have seen in Chapter~\ref{chap:benchmark_results}, the evaluation of Learning-to-Rank methods is spread over the several benchmark datasets. However, as the Learning-to-Rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate.\\

Several studies make a small start in considering Learning-to-Rank method performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and the OHSUMED dataset from LETOR 3.0. To my knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. With a meta-analysis I will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections.

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

LETOR 1.0, LETOR 3.0, Yahoo! Learning to Rank Challenge, WCL2R and AOL have an accompanying paper which was published together with the benchmark collection. As users of those benchmark collections are encouraged to cite these papers, evaluated measurements for these benchmark collections will be gathered through a forward literature search. Table~\ref{tbl:ltr_benchmark_forref} presents an overview of the results of this forward literature search. Google Scholar will be used for this forward reference search.

@@

In contrast to the winning number comparison on LETOR 3.0, there will not be accuracy measurements for each algorithm on each dataset in our meta-analysis. To compare algorithms based on a sparse set of evaluation measurements, a normalised version of the Winning Number metric will be used. This Normalised Winning Number takes into account only those datasets that an algorithm is evaluated on and divides this by the theoretically highest Winning Number that an algorithm would have had in case it it would have been the most accurate algorithm on all datasets on which it has been evaluated. I will redefine the indicator function $I$ in order to only take into account those datasets that an algorithm is evaluated on, as \\

@@

\ac{nDCG}@3, \ac{nDCG}@5, \ac{nDCG}@10 and \ac{MAP} are chosen as metrics on which the meta-analysis will be performed. These metrics seem to be the most frequently used evaluation metrics in most of the used benchmark datasets. An exception are the Yahoo! Learning to Rank Challenge datasets on which mainly \ac{ERR} is used as main evaluation metric. The lack of use of the \ac{ERR}-metric in other benchmarks makes it unsuitable for a cross-benchmark comparison. By making the decision to include \ac{nDCG} at thee cut-off points and only a single \ac{MAP} entry we implicitly attain a higher weight for \ac{nDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting is arbitrary and therefore undesirable, but the number of algorithm evaluation results gained by this makes it a pragmatic approach.

@@

Some studies with evaluation results found through in literature review were not usable for the meta-analysis. The following enumeration lists the properties that made those studies unusable for the meta-analysis, with between brackets the studies that these properties apply to.

@@

Best Single Feature &  & \cite{Gomes2013} & MHR & L2, \cite{Qin2007} &  \\ 

@@

LambdaNeuralRank and CoList both acquired a perfect Normalised Winning Number score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF both scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which can be said to have a higher degree of certainty on the methods' performance because they are validated on three datasets which in addition are more relevant datasets than AOL and Yahoo Set 2 because there are more evaluation results available for the LETOR 3.0 datasets. FenchelRank, OWPC, SmoothRank, DCMP and ListNet are in that order increasingly lower in Normalised Winning Number, but increasingly higher in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.\\

@@

LRUF, FSMRank, FenchelRank, SmoothRank and ListNet showed to be the methods that have no other method superior to them in both Ideal Winning Number and Normalised Winning Number. LRUF is the only methof that achieved this in all \ac{nDCG} comparisons, the \ac{MAP} comparison as well as the cross-metric comparison. With FenchelRank, FSMRank, SmoothRank and ListNet being among the top performing methods in all \ac{nDCG} comparisons as well as in the cross-metric comparison, it can be concluded that the cross-metric results are highly defined by the \ac{nDCG} performance as opposed to the \ac{MAP} performance. This was to be expected, because the cross-metric comparison input data of three \ac{nDCG} entries (@3, @5, and @10) enables it to have up to three times as many as many weight as the \ac{MAP} comparison.\\

@@

LAC-MR-OR and RE-QR showed very good ranking accuracy in the \ac{MAP} comparison on multiple datasets. Both methods Because LAC-MR-OR is only evaluated on two datasets for \ac{nDCG}@10 and RE-QR is not evaluated for \ac{nDCG} at all

\section{Limitations}
In the Normalised Winning Number calculation the weight of each benchmark on the total score is determined by the number of evaluation measurements on this benchmark. By calculating it in this way, we implicitly make the assumption that the Learning-to-Rank methods are (approximately) distributed uniformly over the benchmarks, such that the average Learning-to-Rank method tested are approximately equally hard for each data set. It could be the case however that this assumption is false and that one some datasets significantly better Learning-to-Rank methods are evaluated than on some other datasets.\\

@@

Another limitation lies in the meta-analysis methodology. Using evaluation results published by other researchers relies on the honesty of those researchers. Overly optimistic evaluation results published by other researchers do affect our Normalised Winning Number results. Only including studies in the meta-analysis that comparable show results on one of the baseline methods of a benchmark reduces this limitation but does not solve it. By taking the Ideal Winning Number into account in Figure \ref{fig:normalised_winning_number_all} we further mitigate this limitation, as the Ideal Winning Number is loosely related with the number of studies that reported evaluation results for an algorithm.

>>>>

\label{chap:cross_comparison}
As we have seen in Chapter~\ref{chap:benchmark_results}, the evaluation of Learning-to-Rank methods is spread over several benchmark datasets. However, as the Learning-to-Rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate.\\

Several studies make a small start in considering Learning-to-Rank methods performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and the OHSUMED dataset from LETOR 3.0. To my knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. With a meta-analysis we will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections.

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
With a literature review we will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

LETOR 1.0, LETOR 3.0, Yahoo! Learning to Rank Challenge, WCL2R and AOL have accompanying papers which were published together with these benchmark collections. Users of those benchmark collections are encouraged to cite these papers. Therefore, we collect evaluation measurements of Learning-to-Rank methods on these benchmark collections through forward literature search. Table~\ref{tbl:ltr_benchmark_forref} presents an overview of the results of this forward literature search. Google Scholar will be used to perform the forward reference search.

@@

In contrast to the winning number comparison on LETOR 3.0, there will not be accuracy measurements for each algorithm on each dataset in our meta-analysis. To compare algorithms based on a sparse set of evaluation measurements, a normalised version of the Winning Number metric will be used. This Normalised Winning Number takes only those datasets into account that an algorithm is evaluated on and divides this by the theoretically highest Winning Number that an algorithm would have had in case it it would have been the most accurate algorithm on all datasets on which it has been evaluated. We will redefine the indicator function $I$ in order to only take into account those datasets that an algorithm is evaluated on, as \\

@@

\ac{nDCG}@3, \ac{nDCG}@5, \ac{nDCG}@10 and \ac{MAP} are chosen as metrics on which the meta-analysis will be performed. These metrics seem to be the most frequently used evaluation metrics in most of the used benchmark datasets. An exception is the Yahoo! Learning to Rank Challenge datasets on which mainly \ac{ERR} is used as main evaluation metric. The lack of use of the \ac{ERR}-metric in other benchmarks makes it unsuitable for a cross-benchmark comparison. By making the decision to include \ac{nDCG} at three cut-off points and only a single \ac{MAP} entry, we implicitly attain a higher weight for \ac{nDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting is arbitrary and therefore undesirable, but the number of algorithm evaluation results gained by this makes it a pragmatic approach.

@@

Some studies with evaluation results found through in literature review were not usable for the meta-analysis. The following enumeration enumerates those properties that made one or more studies unusable for the meta-analysis. Between brackets are the studies that these properties apply to.

@@

Best Single Feature &  & \cite{Gomes2013} & \acs{MHR} & \cite{Qin2007} & L2 \\ 

@@

LambdaNeuralRank and CoList both acquired a perfect Normalised Winning Number score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF both scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which can be said to have a higher degree of certainty on the methods' performance because they are validated on three datasets which in addition are more relevant datasets than AOL and Yahoo Set 2 because there are more evaluation results available for the LETOR 3.0 datasets (see Table \ref{tab:ltr_methods_used}). FenchelRank, OWPC, SmoothRank, DCMP and ListNet are in that order increasingly lower in Normalised Winning Number, but increasingly higher in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.\\

@@

LRUF, FSMRank, FenchelRank, SmoothRank and ListNet showed to be the methods that have no other method superior to them in both Ideal Winning Number and Normalised Winning Number. LRUF is the only method that achieved this in all \ac{nDCG} comparisons, the \ac{MAP} comparison as well as the cross-metric comparison. With FenchelRank, FSMRank, SmoothRank and ListNet being among the top performing methods in all \ac{nDCG} comparisons as well as in the cross-metric comparison, it can be concluded that the cross-metric results are highly defined by the \ac{nDCG} performance as opposed to the \ac{MAP} performance. This was to be expected, because the cross-metric comparison input data of three \ac{nDCG} entries (@3, @5, and @10) enables it to have up to three times as many as many weight as the \ac{MAP} comparison.\\

@@

LAC-MR-OR and RE-QR showed very good ranking accuracy in the \ac{MAP} comparison on multiple datasets. Because LAC-MR-OR is only evaluated on two datasets for \ac{nDCG}@10 and RE-QR is not evaluated for \ac{nDCG} at all, LAC-MR-OR and RE-QR are not within the top performing methods in the cross-metric comparison.

\section{Limitations}
In the Normalised Winning Number calculation the weight of each benchmark on the total score is determined by the number of evaluation measurements on this benchmark. By calculating it in this way, we implicitly make the assumption that the Learning-to-Rank methods are (approximately) distributed uniformly over the benchmarks, such that the average Learning-to-Rank method tested are approximately equally hard for each data set. It could be the case however that this assumption is false and that significantly more accurate Learning-to-Rank methods are evaluated on some datasets than on other datasets. \\

@@

Another limitation lies in the meta-analysis methodology. Using evaluation results published by other researchers relies on the honesty of those researchers. Overly optimistic evaluation results published by other researchers do affect our Normalised Winning Number results. Limiting the meta-analysis to those studies that report comparable results on one of the baseline methods of a benchmark set reduces this limitation but does not solve it completely. By taking the Ideal Winning Number into account in Figure \ref{fig:normalised_winning_number_all} we further mitigate this limitation, as the Ideal Winning Number is loosely related with the number of studies that reported evaluation results for an algorithm.
